---
title: "R Notebook"
output: html_notebook
---

 
>  - 📱 Linkedin [Juan Antonio Cabeza Sousa
](https://www.linkedin.com/in/juan-antonio-cabeza-sousa-5b954968/)
>  - 📬 Email:  juaancabsou@gmail.com
>  - 🖥️ Twitter: @[Aceconhielo](https://twitter.com/Aceconhielo)


This notebook is about *Analysing Star Trek Commands*.The data this week comes from [SpeechInteraction.org](http://www.speechinteraction.org/TNG/).

```{r GetData, message=FALSE, warning=FALSE, include=FALSE}
tuesdata <- tidytuesdayR::tt_load('2021-08-17')
tuesdata <- tidytuesdayR::tt_load(2021, week = 34)
computer <- tuesdata$computer
```

```{r Libraries, message=FALSE, include=FALSE}
library(tidyverse, warn.conflicts = FALSE)
library(ggplot2)
library(plotly)
library(DataExplorer)
library(ggpubr)
library(ggchicklet)
library(tidytext)
library(tm)
library(wordcloud)
fontfamily <-"Open Sans"
```


# A glance to the data

Looking the *Data Dictionary* related to this data set and the amount of missing values per column, it helps us to keep just a few important columns for the visualization stage. Those columns (the ones that I will kept for the TidyTuesday visualization) are:
* `char`: Name of the speaking character.
* `char_type`:Either Person or Computer
* `line`: The complete line of dialog (may contain more speech than the speech interaction). Parenthetical are directions and not spoken.
* `type`: The type of interaction, see detailed definitions below.
* `pri_type`: The primary interaction type as defined by the below ranking.
* `domain`: The domain of interaction, see detailed definitions below.
* `sub_domain`: The sub-domain of interaction, generally a specific setting, see below.
* `interaction`: The actual speech interaction. May be shorter or longer than the line of dialog.

I will discard `is_fed`and `error` because their distribution is always the same: TRUE and FALSE respectively. 

```{r EDAWRANGLING, message=FALSE, warning=FALSE, include=FALSE}
chart_intro <- plot_intro(computer)
chart_miss <- plot_missing(computer)
```

```{r EDACHARTS,fig.height=5, fig.width=12,}
ggarrange(chart_intro, chart_miss, ncol = 2, heights = c(10, 10))
```
```{r Infographics Datasets Generator, message=FALSE, warning=FALSE}
# Chart 1: Interactions
interactions <- head(computer %>% filter(char != 'Computer Voice') %>%
  group_by(char) %>%
  count(sort = TRUE),10)

interactions$char <- factor(interactions$char, levels = interactions$char[order(interactions$n)])
colnames(interactions) <- c('Character', 'Interactions')

# Chart 2: Wordclouds
textcleaned <- computer %>%
  unnest_tokens(word, interaction) %>%
  anti_join(get_stopwords(source = "snowball"))

df_wordcloud <- textcleaned %>% group_by(word) %>% count(sort = TRUE)
```



```{r Infographics Chart Generator}

backgroundcolor <- "#264653"
solidchartcolor <- "#e9c46a"
gridlines <- "#006d77"


# Chart 1: Interactions
chartinteractions<-ggplot(data=interactions, aes(x=Character, y=Interactions)) +
  geom_chicklet(stat="identity", color=solidchartcolor, fill=solidchartcolor, width = 0.75, radius = grid::unit(1, 'mm'))+
  geom_text(aes(label=Interactions), hjust=1.6,vjust= 0.25, color=backgroundcolor, size=3.5)+
  theme(
    axis.text.x = element_text(colour = 'white', family=fontfamily),
    axis.title.x = element_text(colour = 'white', family=fontfamily),
    axis.text.y = element_text(colour = 'white', family=fontfamily),
    axis.title.y = element_text(colour = 'white', family=fontfamily),
    panel.background = element_rect(fill = backgroundcolor, colour = backgroundcolor, linetype = "solid"),
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = gridlines), 
    panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = gridlines),
    plot.background = element_rect(fill = backgroundcolor),
    plot.title = element_text(colour="white"),
    plot.margin = unit(c(1,1,1,1), "cm")
  )+
  ggtitle("Users with more interactions")+
  coord_flip()



wordcloudchart <- wordcloud(words = df_wordcloud$word ,
                            freq = df_wordcloud$n,
                            min.freq = 1,max.words=200,
                            random.order=FALSE,
                            rot.per=0.35,
                            colors=brewer.pal(8, "Dark2"))



```


